My title

### 2024-02-13 paper/paper.qmd
Changed file formatting so tables can be presented in paper

library(tidyverse)
library(tidyr)
library(janitor)
library(dplyr)
library(readr)
library(stringr)
```

@@

## Summary statistics.
```{r}
# run code in ***name of script
organized_table_1
```

@@

## Disparities in police awards 
```{r}
#| echo:  false
#| warning: false
#| message: false
 # run script **name 
stargazer(fe_reg_black,fe_reg_female, fe_reg_black_female,fe_reg_blackxfemale, 
          omit =c("hisp", "asian", "natam", "birth_year", "tenure", "tenure2",
          "tenure3", "L_cmpl_civ", "L_cmpl_civ2", "L_cmpl_civ3",
          "L_arrest_total", "L_arrest_total2","L_arrest_total3","L_trr_new",
          "L_trr_new2","L_trr_new3"),
          omit.stat=c("f", "rsq","adj.rsq"),
          add.lines=list(c("Control for"),
                         c("Cohort", "Yes", "Yes", "Yes", "Yes"), 
                         c("Year",  "Yes", "Yes", "Yes", "Yes"), 
                         c("Demographics", " ", " ", "Yes", "Yes"),
                         c("Policing activities", "", "", "Yes", "Yes"),
                         c("Reference group mean",round(mean_white, digits = 2), 
                           round(mean_female_0, digits = 2), 
                           round(mean_white_female_0, digits = 2), 
                           round(mean_white_female_0, digits = 2))), 
          type = 'text')
```

>>>>

library(tidyverse)
library(tidyr)
library(janitor)
library(dplyr)
library(readr)
library(stringr)
library(stargazer)
```

@@

## Summary statistics.
```{r}
# run code in ***name of script
organized_table_1 <- read.csv("~/Police-Award-Nomination-Paper-Reproduction/data/analysis_data/table_1_data.csv")
organized_table_1
```

@@

## Disparities in police awards 
```{r}
#| echo:  false
#| warning: false
#| message: false
 # run script **name

organized_table_2 <- read.csv("~/Police-Award-Nomination-Paper-Reproduction/data/analysis_data/table_2_data.csv")
organized_table_2

```
